Generalised gravitational burst generation with Generative Adversarial Networks

### 2020-04-27 Paper_draft/main.tex
Added comments up to 3.1 and added a makefile

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\bibliographystyle{iopart-num_custom}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{comment}
%\usepackage{subcaptncluon}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, calc}
\expandafter\let\csname equation*\endcsname\relax 
\expandafter\let\csname endequation*\endcsname\relax 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\newcommand{\jordan}[1]{\textbf{\textcolor{red}{JORDAN: #1}}}
\newcommand{\siong}[1]{\textbf{\textcolor{blue}{SIONG: #1}}}
\newcommand{\chris}[1]{\textbf{\textcolor{green}{CHRIS: #1}}}
\newcommand{\michael}[1]{\textbf{\textcolor{orange}{MICHAEL: #1}}}
\begin{document}

@@

\address{University of Glasgow, Physics \& Astronomy Department, Glasgow G12 8QQ, UK}
%\ead{jordan.mcginn@glasgow.ac.uk}
\vspace{10pt}
\begin{indented}
\item[]March 2020
\end{indented}

@@

@@

Gravitational-wave (GW) astronomy is now an established field, starting with the first detection of a binary black hole merger \cite{Abbott2016} on September 2015. Following this, the first and second observations runs (O1 and O2) of Advanced LIGO and Advanced Virgo reported several more mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}. On August 2017 a binary neutron star merger was observed alongside its electron-magnetic counterpart for the first time, giving rise to multimessenger gravitational wave astronomy.

GW bursts are transient signals of typically short duration ($<$ 1s) whose waveforms are not accurately modelled or are complex to re-produce. Astrophysical sources for such transients include: Core collapse supernova, Neutron star instabilities, Fallback accretion onto a neutron star, Non axisymetric deformation in magnetars, Pulsar glitches and Neutron star post-mergers.
As GW bursts are un-modelled they are not sensitive to template based detection schemes such as matched-filtering \cite{Owen1998}, instead, detection involves distinguishing the signal from detector noise. This is only possible if the detector noise is well characterised and the candidate signal can be differentiated from system or environmental glitches. As such, GW burst searches rely on an astrophysical burst signature appearing in multiple detectors.
Many GW burst algorithms \cite{Klimenko_2008, Aso_2008} are tested and tuned using model waveforms that may or may not have astrophysical significance but have easy to define parameters and share characteristics of real bursts that is enough to simulate coincident non-stationary deviations between detectors. Such waveforms may have long-duration, short bandwidth (ringdowns), long-duration, large bandwidth (inspirals) and many algorithms make use of sine-Gaussians: a Gaussian modulated sine wave that is characterised by it's central frequency and narrow bandwidth. This makes it a great tool for diagnosing LIGOs sensitivity to frequency.

We aim to explore the use of machine learning in generating and interpreting these mock GW burst signals. Neural networks have shown to replicate the sensitivities of matched filtering in GW detection \cite{Gabbard2017} and rapid parameter estimation \cite{gabbard2019bayesian}, however these methods have primarily been focused on binary black hole signals and have not yet expanded to burst examples.

@@

A subset of deep learning that has seen fruitful development in recent years \cite{Goodfellow2014} is Generative Adversarial Networks (GANs). These unsupervised algorithms learn patterns in a given training data set using an adversarial process. The generations from GANs are state-of-the-art in fields such as high quality image fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation \cite{reed2016generative} and video prediction \cite{liang2017dual} as well as time series generations \cite{esteban2017realvalued}.

GANs train two competing neural networks, consisting of a discriminator that is set up to distinguish between real and fake data and a generator that produces synthetic
reproductions of the real data. The generator performs a mapping
from an input noise vector \textbf{z} to its representation of the data and the discriminator  maps its
input \textbf{x} to a probability that the input came form either the training
data or generator.  During training, the discriminator is given a batch of samples that contains one half real data
and one half fake data which it then makes predictions on. The
loss for discriminator  is calculated by comparing its predictions to the labelled data through the binary cross-entropy function. The training process
of a GAN alternatively updates the weights of the discriminator  and generator based on information
on its competitors loss function. This loss of discriminator  is used to update the weights
of generator to produce more realistic samples of the input distribution, the loss of G
encourages discriminator  to update its classification abilities. Both networks compete
in a minimax game which generator is trying
minimise and the discriminator is trying to maximise:

\begin{equation}
\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))]
\label{equation:GANloss}
\end{equation}
\subsection{Auxiliary conditional GANs}
In theory, the adversarial process will eventually lead to the local Nash equilibrium \cite{Nash1950} whereby
both neural networks are trained optimally. In practice, however, GANs are
notoriously difficult to train. Such difficulties include: Non-convergence,
where the model parameters oscillate and the loss never converges, mode
collapse where G produces a limited diversity of samples, and diminishing
gradients when applying gradient descent to a
non-continuous function.

To overcome some of these difficulties, a conditional varient of GANs named Conditional-GAN (CGANs) \cite{cgan}
adds structure to the latent space by providing the generator with a class or attribute
label. The generator learns to segment the latent space by clustering distributions which have similar properties, making a point in latent space conditional on a class. This idea was extended further with auxiliary conditional GANs (ACGANs) \cite{odena2016conditional} that require the discriminator to output a
probability of data belonging to each class. A pictorial representation on the differences between these approaches in Figure \ref{fig:gan_comparison}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
GW burst signals remain an unmodelled phenomenon, as such, current detection algorithms focus on waveform reconstruction reliant on coincident signals within multiple detectors. We propose a signal generation scheme utilizing GANs trained on burst-like waveforms. The GAN is trained on five signal morphology's spanning a range of prior parameters. The families are:

@@

\begin{itemize}
	\item Sine-Gaussian:
		\begin{equation}
		\label{eqn:sg}
			h(t) = A \exp\bigg[ - \frac{(t-t_{0})^2}{\tau^2} \bigg] \sin (2 \pi f_0 (t-t_0))
		\end{equation}	
		where $f_0$ is the central frequency that takes values between 30 Hz - 50 Hz. $\tau$ is the decay parameter chosen to be between 60s$^{-1}$  and 15s$^{-1}$ and the starting epoch chosen between 0.2s - 0.8s. Sine-Gaussian waveforms have a similar form to those produced by the merger of two black holes. Although binary mergers tend to be longer in duration.  		
	\item Ring-down:
		\begin{equation}
			h(t) = A \exp \bigg[-\frac{(t-t_0)}{\tau}\bigg]\sin(2 \pi f_0 (t-t_0))
		\end{equation}
		For ring-down signals the parameters for $f_0, \tau, t_0$ are chosen between; 30 Hz-50Hz, 0.02-0.1 and 0.1s-0.8s respectfully. These signals aim to replicate the post-merger late stages of binary coalescence.
	\item White-noise bursts:\hfill \\
	These signals are produced by inserting samples of random Gaussian noise with zero mean and a variance of 0.1 at a random point between 0.2s - 0.8s. The source of this signal type can be attributed to core-collapse supernova. 
	\item Gaussian:\\
	A simple Gasssian waveform with $t_0$ ranging from 0.2s to 0.8s and $\tau$ between  100$^{-1}$ and 20$^{-1}$
	\item Binary black holes (BBH): \\
	BBH signals are simulated using IMRPhenomD waveform routine from LALSuite which models the inspiral, merger and ringdown of a BBH waveform. The component masses lie in the range of [5,70]M$_0$ with zero spins and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power law with index of 1.6 https://arxiv.org/abs/1811.12940. The signals are generated using random right ascensions and declinations uniform over the sky and the inclinations are drawn from the cosine of a uniform distribution in the range [-1,1]. The peaks of the waveforms are set to be within [0.75,0.95]s of the 1s time interval. 
\end{itemize}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/train_gen.pdf}
    \caption{Examples of simulated burst gravitational wave signals. Top row shows examples from the training set. From left to right: Sine-Gaussian, Ringdown, White-noise burst, Gaussian, Binary black hole merger. The bottom row shows the conditional generations from the GAN. }
    \label{fig:train}
\end{figure}

@@

Given a 100 dimensional vector drawn from a normal distribution, a class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set. We set out by describing the quality of generated waveforms and how they compare to the training set. We then explore the structure of the latent and class spaces by interpolating between points in these spaces. We test vector arithmetic that can be used to generate a new breed of signal by merging two or more families together. Finally, we discuss the capacity of the discriminator as a GW burst classifier and the auxiliary component of this work.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this work we present the potential of Generative Adversarial Networks for burst gravitational wave analysis. We have shown that GANs have the ability to generate 5 class varieties of modelled burst GW signals that can be generated at whim. The latent and class spaces were explored through interpolation and suggest that the space provides smooth translations between classes and overall waveform shape. We then showed targeted waveform generation by mixing classes to produce new unmodlled waveform varieties that can be used to test current burst search pipelines. \jordan{couple of sentences about classifier}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\bibliographystyle{iopart-num_custom}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{comment}
\usepackage{acronym}
%\usepackage{subcaptncluon}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, calc}
\expandafter\let\csname equation*\endcsname\relax 
\expandafter\let\csname endequation*\endcsname\relax 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\newcommand{\jordan}[1]{\textbf{\textcolor{red}{JORDAN: #1}}}
\newcommand{\siong}[1]{\textbf{\textcolor{blue}{SIONG: #1}}}
\newcommand{\chris}[1]{\textbf{\textcolor{green}{CHRIS: #1}}}
\newcommand{\michael}[1]{\textbf{\textcolor{orange}{MICHAEL: #1}}}
\newcommand{\dcc}{LIGO-PXXXXXXX}
\input{tag.tex}
\begin{document}

@@

\address{University of Glasgow, Physics \& Astronomy Department, Glasgow G12 8QQ, UK}
%\ead{jordan.mcginn@glasgow.ac.uk}
\vspace{10pt}
\begin{indented}
\item[]\commitDATE\\\mbox{\small \commitID}\\\mbox{\dcc}
\end{indented}

@@

\acrodef{GW}[GW]{gravitational wave}
\acrodef{GAN}[GAN]{generative adversarial networks}
\acrodef{CGAN}[CGAN]{conditional generative adversarial networks}
\acrodef{ACGAN}[ACGAN]{auxilliary conditional generative adversarial networks}
\acrodef{BBH}[BBH]{binary black hole}

@@

% introduce \ac{GW} astrophsyics
%
\ac{GW} astronomy is now an established field, starting with the first
detection of a binary black hole merger \cite{Abbott2016} in September 2015.
Following this, the first and second observations runs (O1 and O2) of Advanced
LIGO and Advanced Virgo~\chris{need refs for the detectors, see here
https://pnp.ligo.org/ppcomm/standard\_references.html} reported several more
mergers \cite{Abbott2016a, Abbott2017, Abbott2017a, Abbott2017b}. On August
2017 a binary neutron star merger was observed alongside its electromagnetic
counterpart for the first time, giving rise to multimessenger gravitational
wave astronomy.

% introduce burst searches
%
GW bursts are transient signals of typically short duration ($<$ 1s) whose
waveforms are not accurately modelled or are complex to re-produce.
Astrophysical sources for such transients include: Core collapse supernova,
Neutron star instabilities, Fallback accretion onto a neutron star, Non
axisymetric deformation in magnetars, Pulsar glitches and Neutron star
post-mergers.  As \ac{GW} bursts are un-modelled they are not sensitive to
template based detection schemes~\chris{OK, but logically dodgy. You make it
sound like we could use a template scheme but it would be insensitive. The
point is that we don't have templates in the first place.} such as
matched-filtering \cite{Owen1998}, instead, detection involves distinguishing
the signal from detector noise. This is only possible if the detector noise is
well characterised and the candidate signal can be differentiated from
systematic or environmental glitches. As such, \ac{GW} burst searches rely on
an astrophysical burst signature appearing in multiple detectors~\chris{at
similar times?}.

% Discuss the family of burst waveforms currently used and why - not in detail, just
% an introduction 
%
Many \ac{GW} burst algorithms \cite{Klimenko_2008, Aso_2008}~\chris{many? needs
more than 2 refs for many.} are tested and tuned using model waveforms that may
or may not have astrophysical significance but have easy to define parameters
and share characteristics of real bursts that is enough to simulate coincident
non-stationary deviations~\chris{fancy sounding but I'm not sure what
non-stationary deviations means.} between detectors. Such waveforms may have
long-duration, short bandwidth (ringdowns), long-duration, large bandwidth
(inspirals) and many algorithms make use of sine-Gaussians: a Gaussian
modulated sine wave that is characterised by it's central frequency and narrow
bandwidth.~\chris{not the time to try to describe the types of burst waveforms.
Also, be careful with satying things like ringdowns have narrow bandwidth. I
know we specify a single frequency but becuase of the short duration, the
signal is broad band. Look at the FFT} This makes it a great tool for
diagnosing LIGOs sensitivity to frequency.~\chris{strange unfinished sentence.}

% Introduce ML techniques in GWs
%
\chris{Introduce ML techniques in GWs}

% What this paper does on GANs in 1 paragraph
%
\chris{What this paper does on GANs in 1 paragraph}

% the point of the paper
%
\chris{describe the structure of the paper}
We aim to explore the use of machine learning in generating and interpreting
these mock \ac{GW} burst signals. Neural networks have shown to replicate the
sensitivities of matched filtering in \ac{GW} detection \cite{Gabbard2017} and rapid
parameter estimation \cite{gabbard2019bayesian}, however these methods have
primarily been focused on binary black hole signals and have not yet expanded
to burst examples.~\chris{OK, thanks for the referdndes but you should probably
have more refs to other ML GW papers. I think you should dedicate at least one
paragrpah to GW ML efforts. The final paragrapgh of the section should
introduce the paper structure. The penultimate paragraph should expain what the
point of this paper is - in non technical terms. This is all outlined in the
bullet points (hidden) at the start of this section.}

@@

% introduce GANs
%
A subset of deep learning that has seen fruitful development in recent years
\cite{Goodfellow2014} is \acp{GAN}. These unsupervised algorithms learn
patterns in a given training data set using an adversarial process. The
generations from \acp{GAN} are state-of-the-art in fields such as high quality image
fidelity \cite{brock2018large,karras2019analyzing}, text-to-image translation
\cite{reed2016generative} and video prediction \cite{liang2017dual} as well as
time series generations \cite{esteban2017realvalued}.

% How a GAN works
%
\acp{GAN} train two competing neural networks, consisting of a discriminator
that is set up to distinguish between real and fake data and a generator that
produces synthetic reproductions of the real data. The generator performs a
mapping from an input noise vector $\mathbf{z}$ to its representation of the
data and the discriminator maps its input $\mathbf{x}$ to a probability that
the input came form either the training data or generator.  During training,
the discriminator is given a batch of samples that contains one half real data
and one half fake data which it then makes predictions on. The loss for the
discriminator is calculated by comparing its predictions to the labelled data
through the binary cross-entropy function. The training process of a \ac{GAN}
alternatively updates the weights~\chris{too much knowledge assumed - what are
weights, they haven't been defined} of the discriminator and generator based on
information on its competitors loss function. This loss of discriminator is
used to update the weights of the generator to produce more realistic samples
of the input distribution, the loss of G~\chris{what is G?} encourages the
discriminator to update its classification abilities. Both networks compete in
a minimax game~\chris{what is a minimax game? references?} which the generator
is trying to minimise and the discriminator is trying to
maximise:~\chris{nicely written, however, it needs an extra 25\% explanation
for people not familar with ML or GANs in particular. Try to spell things out
more. Also refer to Fig 1 somewhere in this section.}
%
\begin{equation}
\mathop{\text{min}}_{G}  \mathop{\text{max}}_{D} V(D,G) = \mathbb{E}_{\mathbf{x} \sim p_{\text{r}}(\mathbf{x})} [\text{log} D(\mathbf{x})] \\ + \mathbb{E}_{\mathbf{z} \sim p_{\text{z}}(\mathbf{z})} [\text{log}(1-D(G(\mathbf{z})))]
\label{equation:GANloss}
\end{equation}
%
~\chris{In line with explanding the explanation a bit more, really take the time
to state what controls the functions and also deine ALL mathematical variables.
What are $D, G, V\ldots$ Why are you taking the logs? What situation so you
start with? What do you end up with? This is a nice start but beef it up.}

\subsection{Auxiliary conditional GANs}

% describing the problems with GANs 
%
In theory, the adversarial process will eventually lead to the local Nash
equilibrium \cite{Nash1950} whereby both neural networks are trained
optimally~\chris{this statement and this paragraph should be stated in the
previous section}.  In practice, however, \acp{GAN} are notoriously difficult
to train. Such difficulties include: Non-convergence, where the model
parameters~\chris{you haven't stated what the model parameters are yet}
oscillate and the loss~\chris{the reader soes not know what the loss is and
what the point of it is} never converges, mode collapse where G produces a
limited diversity of samples~\chris{samples of what?}, and diminishing
gradients when applying gradient descent to a non-continuous
function~\chris{not sure about what non-continuous means here but in general
you are bringing in too many concepts without explanation e.g., gradient
descent, why is that relevant? the reader does not know.}.

% introduce CGANs and ACGANs
%
To overcome some of these difficulties, a conditional variant of \acp{GAN}
named \acp{CGAN}~\cite{cgan} adds structure to the latent space~\chris{what is
the latent space - you called it an input noise vector before} by providing the
generator with a class or attribute label. The generator learns to segment the
latent space by clustering distributions which have similar properties, making
a point in latent space conditional on a class~\chris{are we sure about this?
all classes share the same latent space and I don't think that the space gets
segmented into areas corresponding to different classes - I do think that it
gets broken down into spaces with different intrinsic physical properties e.g.,
high frequency, long duration, etc...}. This idea was extended further with
\acp{ACGAN}~\cite{odena2016conditional} that require the discriminator to
output a probability of data belonging to each class. A pictorial
representation on the differences between these approaches is shown in
Fig.~\ref{fig:gan_comparison}.

@@

\chris{this section is supposed to be on ACGANs but it only mentions them in
the final sentence. Again, like the previous section, a bit more explanation
would be good. Does ths maths change? Could you have a new version of Eq 1 for
CGANs and ACGANs? Also, if would be good to have a statement that you will be
using one of these methods in this paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% introduce the training data
%
\ac{GW} burst signals remain an unmodelled phenomenon, as such, current
detection algorithms focus on waveform reconstruction reliant on coincident
signals within multiple detectors~\chris{burst detection algorithms do not need
waveform reconstruction for searches - it is an add on feature.}. We propose a
signal generation scheme utilizing~\chris{utilizing certainly is fancier than
using. Dont go overboard with the language.} \acp{GAN} trained on burst-like
waveforms. The \ac{GAN}~\chris{is it a GAN or is it a CGAN or an ACGAN? Be
clearer} is trained on five signal morphology's spanning a range of prior
parameters. The families are:~\chris{I know they don't all share the same
parameters but it might be sensible to make a table of the prior ranges rather
than haviong it all stated in text.}
%
\begin{itemize}
%
\item Sine-Gaussian:\\
\chris{don't just start things with an equation}		
%
\begin{equation}
\label{eqn:sg}
h(t) = A \exp\bigg[ - \frac{(t-t_{0})^2}{\tau^2} \bigg] \sin (2 \pi f_0 (t-t_0))
\end{equation}	
%		
where $f_0$ is the central frequency that takes values between 30 Hz - 50 Hz.
$\tau$ is the decay parameter chosen to be between 60s$^{-1}$  and 15s$^{-1}$
and the starting epoch chosen between 0.2s - 0.8s. Sine-Gaussian waveforms have
a similar form to those produced by the merger of relatively high mass binary
black holes for which the inspiral phase occurs at frequencies below
ground-based detector sensitivities.
%
\item Ring-down:\\
\chris{don't just start things with an equation}
%
\begin{equation}
h(t) = A \exp \bigg[-\frac{(t-t_0)}{\tau}\bigg]\sin(2 \pi f_0 (t-t_0))
\end{equation}
%		
For ring-down signals the parameters for $f_0, \tau, t_0$ are chosen between;
30 Hz-50Hz, 0.02-0.1 and 0.1s-0.8s respectfully. These signals aim to replicate
the post-merger late stages of binary coalescence.
%
\item White-noise bursts:\\
\chris{where is the waveform equation?}
These signals are produced by inserting samples of random Gaussian noise with
zero mean and a variance of 0.1 at a random point between 0.2s - 0.8s. The
source of this signal type can be attributed to core-collapse
supernova~\chris{is this correct? these waveofms are approximations so best not
to say that they correspond directly to physical phenomena}.
%
\item Gaussian pulse:\\
\chris{where is the waveform equation?}
A simple Gasssian pulse waveform with $t_0$ ranging from 0.2s to 0.8s and
$\tau$ between  100$^{-1}$ and 20$^{-1}$

\item Binary black holes (BBH): \\
\ac{BBH} signals are simulated using IMRPhenomD waveform routine from
LALSuite~\chris{references for both the waveofrm and lalsuite} which models the
inspiral, merger and ringdown of a \ac{BBH} waveform. The component masses lie
in the range of [5,70]M$_0$~\chris{not $M_0$ but $M_{\odot}$} with zero spins
and we fix m$_1$ $>$ m$_2$. The mass distribution is approximated by a power
law with index of 1.6 https://arxiv.org/abs/1811.12940~\chris{correct;ly
reference this}. The signals are generated using random right ascensions and
declinations uniform over the sky and the inclinations are drawn from the
cosine of a uniform distribution in the range [-1,1]. The peaks of the
waveforms are set to be within [0.75,0.95]s of the 1s time interval.~\chris{for
all the signal models please check that the prior ranges and distributions are
consistent with the presented results.} 
%
\end{itemize}

\chris{you seem to be missing a description of the antenna patterns and time
delay that you apply to each waveform. It should go here. You should also
include all other technical information like how you normalise the amplitudes
and how you select random sky positions, how the data is represented to the
network (as an image or as channels) how many detectors do you use? etc... }

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/train_gen.pdf}
    \caption{Examples of simulated \ac{GW} burst signals. Top row shows
examples from the training set. From left to right: Sine-Gaussian, Ringdown,
White-noise burst, Gaussian pulse, Binary black hole merger. The bottom row
shows the conditional generations from the GAN.~\chris{slightly more
explanation. The reader may be concerned that the top and bottom do not look
the same. Should they? They may wonder why is there only one waveform and not
one per detector?} } \label{fig:train} \end{figure}

@@

Given a 100 dimensional vector drawn from a normal distribution, a class label and sky localisation information, the GAN is able to generate burst-like waveforms  generalised from the training set. We set out by describing the quality of generated waveforms and how they compare to the training set. We then explore the structure of the latent and class spaces by interpolating between points in these spaces. We test vector arithmetic that can be used to generate a new breed of signal by merging two or more families together. Finally, we discuss the capacity of the discriminator as a \ac{GW} burst classifier and the auxiliary component of this work.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In this work we present the potential of Generative Adversarial Networks for burst gravitational wave analysis. We have shown that GANs have the ability to generate 5 class varieties of modelled burst \ac{GW} signals that can be generated at whim. The latent and class spaces were explored through interpolation and suggest that the space provides smooth translations between classes and overall waveform shape. We then showed targeted waveform generation by mixing classes to produce new unmodlled waveform varieties that can be used to test current burst search pipelines. \jordan{couple of sentences about classifier}.
